Target Speaker Extraction using Discrete Representations from Self-Supervised Models and Language Models \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-09-04 src/paper.tex
update

\subsubsection{Cross Attention}
One of the key factors in target speaker extraction is to 
inject the information of target speaker 
into the mixture. Spex+ \cite{spex_plus} jointly trains a speaker verification task module 
besides the separator, which might not be optimal for the separator task \cite{sef_net}. SEF-Net \cite{sef_net} has proposed an speaker embedding free way to inject the 
target speaker information into the mixture by using cross attention module, and it has 
achieved superior performance compared to other methods. Therefore, we apply 
the cross attention module to inject the reference embedding into the mixture. The details 
are in Fig.\ref{cross_attention}.
The cross attention module consists of a positional 
embedding layer, a cross-multiple head attention module, 
and a FiLM module. 
We use \(E_m\) as query and \(E_r\) as key and value for 
the attention module. The output of the cross-multiple head attention module \(E_{spk}\)
is passed together with \(E_m\) to get the final output of the module.

>>>>

\subsubsection{Cross Attention}
One of the key factors in target speaker extraction is to 
inject the information of target speaker 
into the mixture. Spex+ \cite{spex_plus} jointly trains a speaker verification task module 
besides the separator, which might not be optimal for the separator task \cite{sef_net}. SEF-Net \cite{sef_net} has proposed an speaker embedding free way to inject the 
target speaker information into the mixture by using cross attention module, and it has 
achieved superior performance compared to other methods. Therefore, we apply 
the cross attention module to inject the reference embedding into the mixture. The details 
are in Fig.\ref{cross_attention}.
The cross attention module consists of a positional 
embedding layer, a cross-multiple head attention module, 
and a FiLM module. 
We use \(E_m\) as query and \(E_r\) as key and value for 
the attention module. The output of the cross-multiple head attention module \(E_{spk}\)
is passed together with \(E_m\) to the feature-wise linear modulation (FiLM) get the final output of the module. The output of 
FiLM is denoted as
